\documentclass{article}
    \usepackage{fancyhdr}
    \usepackage[top=1in, bottom=0in, left=0.7in, right=0.7in]{geometry}
    \usepackage[hidelinks]{hyperref}\hypersetup{
        allcolors = black
    }
    
    \usepackage{enumitem} 
    \usepackage{multicol}
    \usepackage{fontawesome}
    \setlist{leftmargin=1cm,labelindent=1cm,itemsep=1.4pt,parsep=0pt}
    \renewcommand{\familydefault}{\sfdefault}
    \renewcommand{\headrulewidth}{.5pt}
    \renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$} % make bullets smaller
    
    \pagestyle{fancy}
    \chead{\LARGE{\textbf{Lucas Burns}}\\ \vspace{0.085in} \normalsize 
    \href{https://lucas.burns.io/}{\faicon{link}}\hspace{0.085in}
    \href{https://www.github.com/BurnsCommaLucas}{\faicon{github}}\hspace{0.085in}
    \href{https://www.linkedin.com/in/burnscommalucas/}{\faicon{linkedin}}
    }
    \lhead{\href{mailto:lucas@burns.io}{\large \textit{lucas@burns.io}} }
    \rhead{\large \textit{253.279.3332}}
\begin{document}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\subsubsection*{Experience}

    \begin{description}
		
	\item[Senior Backend Engineer,] \hfill \textit{Jan. 2022 — Present}
	\item[Backend Engineer] \hfill \textit{Feb. 2020 — Jan. 2022}
		
        \textit{Driveway, Portland, OR}
        \begin{itemize}
        \item Design and implement a flexible search API for over 50,000 vehicles across 250 dealerships using MongoDB Atlas.
        \item Architect and develop specialized Kotlin microservices to support user shopping flows.
        \item Build and deploy IaC alongside microservices using Terraform, Datadog, and Microsoft Azure.
        \item Mentor software development interns and incoming junior developers.
        \end{itemize}
        \textit{Technologies:} Kotlin, Spring, GraphQL, MongoDB \& Atlas Search, PostgreSQL, Terraform, Kubernetes, Azure
		\vspace{0.5em}

	\item[Full Stack Software Engineer] \hfill \textit{Nov. 2017 — Feb. 2020}
		
        \textit{EVRAZ North America, Portland, OR}
        \begin{itemize}     
            \item Update and improve desktop, terminal, and web applications.
            \item Maintain monolithic legacy steel mill software tools for internal and external users.
            \item Collaborate with developers and customers to gather requirements and centralize business knowledge.
        \end{itemize}
        \textit{Technologies:} Java, Spring, Angular, Typescript, C, SQL
        
    \end{description}
%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\subsubsection*{Projects and Accomplishments}
    \begin{description}

        \item[\href{https://driveway.com/shop}{Driveway.com:\hspace{0.075in}\faicon{link}}] Various APIs to support vehicle shopping flows.
            \begin{itemize}
                \item Built using Kotlin, Spring, MongoDB, PSQL, and GraphQL with CI/CD through Azure DevOps and Kubernetes/Helm.
                \item Services include: real-time inventory search \& syndication systems, photo aggregation service, tax \& fee gateway, checkout flow orchestrator service.
                \item Systems contain ETL processes, messaging systems, and live APIs from multiple third party sources to provide a curated shopping experience.
            \end{itemize}

            \vspace{0.5em}
        \item[\href{https://www.github.com/BurnsCommaLucas/ready-botlin}{Ready-Bot:\hspace{0.075in}\faicon{link}}] A ready-check bot for Discord servers.
            \begin{itemize}
                \item Built using the Discord4J framework, verified by Discord, and active in 650+ unique Discord servers.
                \item Deployed to Linode with automatic builds via GitHub \& Jenkins.
                \item Integrates with MongoDB for persistent and redundant storage.
            \end{itemize}

            \vspace{0.5em}

        \item[\href{https://github.com/BurnsCommaLucas/API-Scout}{API-Scout:\hspace{0.075in}\faicon{link}}] Mac native API testing tool.
            \begin{itemize}
            	\item Built using in Swift with SwiftUI.
            	\item Made as an exercise in both Swift and Mac native software development.
            \end{itemize}

            \vspace{0.5em}

        \item[Miscellaneous:] \hfill
            \begin{itemize}
                \item Able to solve a 3$\times$3 puzzle cube, best solve time 57 seconds.
                \item Proficient in 8 musical instruments.
                \item Eagle Scout, BSA.
        \end{itemize}
    \end{description}

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\subsubsection*{Technical Skills}
    \begin{description}    
        \item[Languages/Frameworks:] 
            Java, 
            Kotlin,
            Spring,
            GraphQL,
            Typescript,
            Angular,
            Swift,
            Python,
            C,
            C\#,
            OpenGL

            \vspace{0.5em}

        \item[Tools:] 
            Unix,
            Shell,
            Git,
            SQL,
            NoSQL,
            Azure,
            Kubernetes,
            Jenkins,
            Maven,
            Gradle,
            Unity,
            Blender
    \end{description}
    
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\subsubsection*{Education}
    \begin{description}
        \item[B.S. Computer Science, Mathematics Minor]\hfill \textit{2013 - 2017}

        \textit{University of Portland, Portland, OR}

%        \vspace{0.5em}

%        \item[Coursework:]
%            Computer Networks, 
%            Artificial Intelligence, 
%            Computer Graphics, 
%            Analysis of Algorithms,
%            Statistics \& Probability,
%            Linear Algebra
    \end{description}
    
    \begin{center}
	\vspace{.25in}
    \href{https://www.github.com/BurnsCommaLucas/Resume}{\small Built with \LaTeX \hspace{0.001in} \& Pandoc \faicon{github}}
    \end{center}

\end{document}
